Applied Measure Theory for Probabilistic Modeling

### 2022-05-11 paper/paper.tex
edits

A key observation is that having defined probability mass for a number of relatively simple sets, for example on all intervals,
Kolmogorov's axioms give a recipe to compute the probability mass of more complicated sets, and with those, even more in new applications of the axioms, etc.
One says the $\sigma$-algebra is \emph{generated} by these sets.
Indeed, \verb|Distributions.jl| does not give means to compute probability for arbitrary subsets of floating point numbers,
but gives a way of computing probability mass just of intervals of the form $(-\infty, x]$ throught the function \verb|cdf|.

For spaces that are ``small enough'', it is in fact possible to assign meaningful probabilities to all subsets of the space. Unfortunately, this is impossible for any space containing a continuum such as the real line. Just representing a single arbitrary subset of the \verb|Float64|-range, the computational abstraction of the real line, would require staggering 2\,306 Petabytes of memory. This is not practical.

>>>>

A key observation is that having defined probability mass for a number of relatively simple sets, for example on all intervals,
Kolmogorov's axioms give a recipe to compute the probability mass of more complicated sets, and with those, even more in new applications of the axioms, etc.
One says the $\sigma$-algebra is \emph{generated} by these sets.
Indeed, \verb|Distributions.jl| does not give means to compute probability for arbitrary subsets of floating point numbers,
but gives a way of computing probability mass just of intervals of the form $(-\infty, x]$ through the function \verb|cdf|.

For spaces that are ``small enough'', a meaningful probability can be assigned to each subset of the space. Unfortunately, this is impossible for any space containing a continuum such as the real line. Just representing a single arbitrary subset of the \verb|Float64|-range, the computational abstraction of the real line, would require staggering 2\,306 Petabytes of memory. This is not practical.
